Parallel multi-objective optimization using selective operation application islands

### 2017-05-17 hpmoon-coor.tex
Changed title and abstract to avoid the coevolutionary cooperative term

\title{Parallel multi-objective optimization using co-evolutionary
  islands with overlapping search space}
% New title suggestion
% Should coevolutionary go somewhere? Are they coevolutionary? - jj

@@

One of the most extended
methods are the distributed co-evolutionary algorithms, where each
processor deals only with a part of the decision space, that is, the
individuals belonging to the same sub-population (island) explore the
same subset of decision variables. These subsets are usually disjoint
sets. We have previously proved that extending the length of these
subsets, and therefore, sharing some search space between islands,
implies an improvement in the results.

In this paper, a new method to
automatically adapt the size of the overlapping, or shared, sections
of the individuals has been compared to other collaborative
evolutionary techniques. Different number of islands, chromosome sizes
and problems have been used. The analysis of the obtained experimental
results, by using different metrics, shows that coevolutionary
approaches can provide statistically significant improvements with
respect to the base algorithm, being the method to automatically adapt
the overlapping size the one to obtain the best performance during the
same execution time. Results also show that the relation of the number
of islands (subpopulations) to the length of the chromosome (number of
decision variables) is also a relevant factor to determine the most
efficient alternative to distribute the decision variables. 
\end{abstract}

\begin{keyword}
Multi-objective algorithms \sep coevolution \sep NSGA-II  \sep distributed evolutionary algorithms \sep Island model
\end{keyword}

>>>>

\title{Parallel multi-objective optimization using selective operation application
  islands}
% New title suggestion
% Should coevolutionary go somewhere? Are they coevolutionary? - jj
% PABLO: Renaming again to avoid using the coevolutionary and cooperative

@@

One of the most extended
methods are the distributed co-evolutionary algorithms, where each
processor deals only with a part of the decision space, that is, the
individuals belonging to the same sub-population (island) explore the
same subset of decision variables. However, these methods only works with decomposable problems.

A similar idea is presented here to deal with un-decomposable problems: 
instead of sharing parts of individuals, each processor applies the variation 
operators to a specific subset of the whole individual. We have previously proved 
that extending the length of these subsets, and therefore, sharing some search 
space between islands, implies an improvement in the results.

In this paper, a new method to
automatically adapt the size of the overlapping, or shared, sections
of the individuals has been compared to other collaborative
evolutionary techniques. Different number of islands, chromosome sizes
and problems have been used. The analysis of the obtained experimental
results, by using different metrics, shows that selective operation application
approaches can provide statistically significant improvements with
respect to the base algorithm, being the method to automatically adapt
the overlapping size the one to obtain the best performance during the
same execution time. Results also show that the relation of the number
of islands (subpopulations) to the length of the chromosome (number of
decision variables) is also a relevant factor to determine the most
efficient alternative to distribute the decision variables. 
\end{abstract}

\begin{keyword}
Multi-objective algorithms \sep NSGA-II  \sep distributed evolutionary algorithms \sep Island model
\end{keyword}
